---
title: "Scrape Wiktionary Words"
author: "Egemen"
date: "07 11 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## These are the necessary libraries! 
## Before you start, add SelectorGadget Chrome Extension to your Browser
## Link: https://chrome.google.com/webstore/detail/selectorgadget/mhjhnkcfbdhnjickkkdbjoemdmbfginb
## Watch a video of how to use the SelectorGadget: https://www.youtube.com/watch?v=YdIWI6K64zo
## It's super simple. When you're done, run the codes!

```{r}
library(rvest)
library(tidyverse)
library(rversions)
library(dplyr)
```

## We are using our link list from Step 1.
## Make sure the .Rmd file is at the same folder with the CSV.
## If not, change it to ---> wkt_links <- read.csv("wherever the CSV is in your computer")

```{r}
wkt_links <- read.csv("wiktionary_page_link.csv")
  wkt_links <- wkt_links[[2]]

wkt_links
```

## We are using our link list from Step 1.
## Pay attention to step '4. parse content'. That's the part SelectorGadget really does it's trick!

```{r}
# 1. Storing the content in an Empty Dataframe
allcontent <- data.frame()

# 2. Writing a loop for Parsing

for (i in wkt_links){
  print(i)
  
  # 3. read the page just once
  page<-read_html(i)

  # 4. parse content
  wkt_words <- page %>% html_nodes('#mw-pages li') %>% html_text()
    
  # 5. dataframe to store data from this loop
  alldf <- data.frame(wkt_words)
  
  # 6. combine temp with all data
  allcontent<-rbind(allcontent, alldf)  
  
}
```

## Let's check if everything with our DataFrame is okay:

```{r}
allcontent

```

## If so, let's store it in to a CSV and there we are!
## Congratulations, you have a word list now.

```{r}
write.csv(alldf)
```

